Documentation/overview Functional Limits of Agreement

### 2021-12-07 man/floa_doc.Rmd
Move files to man folder

---
title: "Documentation/overview Functional Limits of Agreement"
author:
  - name: Daniel Koska
    email: daniel.koska@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
    footnote: Corresponding Author
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: github_document
# output:
#   html_document: 
#     keep_md: yes
#     theme: united
#     toc: yes
#     toc_float: yes
---

>>>>

---
title: "Documentation/overview Functional Limits of Agreement"
author:
  - name: Daniel Koska
    email: daniel.koska@hsw.tu-chemnitz.de
    affiliation: Chemnitz University of Technology, Research Methodology and Data Analysis in Biomechanics
    footnote: Corresponding Author
date: "`r format(Sys.time(), '%d %B, %Y')`"
# output: github_document
output:
  html_document:
    keep_md: yes
    theme: united
    toc: yes
    toc_float: yes
---
